### 2018-07-13 poster/poster.tex
poster

  \headerbox{Contributions}{name=contribution,column=0,below=motivation}{
  \noindent \begin{enumerate}\compresslist
		\item A formalization of the hierarchical dispatching algorithm
		\item Hierarchical overriding: override individual branches of the class hierarchy.
		\item FHJ: a formalized model based on Featherweight Java
		\item Prototype implementation: FHJ interpreter in Scala.
   \end{enumerate}
   \vspace{0.3em}
  }
\begin{comment}
  \headerbox{Implementation}{name=implementation,column=0,below=contribution}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Java supports compilation agents, where Java libraries can interact with the Java compilation process,
acting as a man in the middle between the
generation of AST and bytecode.

This process is facilitated by frameworks like Lombok:
a Java library that aims at reducing Java boilerplate code via
annotations. \mixin was created using Lombok.

\noindent{\centering\includegraphics[width=\linewidth]{pdfs/lombok3.png}\\}
\vspace{0.1em}
}

  \headerbox{UML Diagram}{name=uml,column=0,below=implementation}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent{\centering\includegraphics[width=0.8\linewidth]{pdfs/PegasusDetail.pdf}\\}
\vspace{0.1em}
}

  \headerbox{Results (Partial)}{name=result,column=0,below=uml,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the maze game case study, both SLOC and \# of interfaces are greatly reduced:
\noindent{\centering\includegraphics[width=0.81\linewidth]{pdfs/result.png}\\}
\vspace{0.1em}
}
\end{comment}

\vspace{-0.5em}
\headerbox{Object Interfaces and Instantiation}{name=Model,column=1,span=2,row=0}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lstinputlisting[linerange=6-13]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
% \lstinputlisting[linerange=17-19]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_INST
\lstinputlisting[linerange=8-12]{../UseMixinLombok/src/pegasus/simple/lombok/Main.java}% APPLY:linerange=PEGASUS_LOMBOK
\lstinputlisting[linerange=1-5]{./import_src/src1.txt}
}

\vspace{-0.5em}
\headerbox{Object Interfaces with State (immutable data)}{name=results,column=1,span=2,row=0,below=Model}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \begin{multicols}{2}
%  \noindent{\centering\includegraphics[width=1\linewidth]{images/mymodel.pdf}\\}
% The process of generating an academic document is as follows: for each citation in that document, firstly sample a topic $\topic_k$ according to the distribution from paper\_topic distribution $\delta(\topic ; \paper)$ or author\_topic distribution $\zeta(\topic ; \authorvar)$ or venue\_topic distribution $\psi(\topic ; \venue)$  based on the document type. Then, draw a citation $\citationvar$ from the sampled topic distribution $\phi(:;\topic_k)$ in topic\_citation distribution $\phi(\citationvar;\topic)$.
% \end{multicols}

\lstinputlisting[linerange=7-11]{./import_src/src1.txt}
\lstinputlisting[linerange=13-15]{./import_src/src1.txt}
}

@@

\headerbox{with- Methods}{name=with,column=1,span=2,row=0,below=results}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lstinputlisting[linerange=1-5]{./import_src/src2.txt}
}

\vspace{-0.5em}
\headerbox{Mutable Data \& Field Type Refinement}{name=refine,column=1,span=2,row=0,below=with}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lstinputlisting[linerange=7-10]{./import_src/src2.txt}
}
\vspace{-0.5em}

\headerbox{More in the paper}{name=more,column=1,span=2,row=0,below=refine}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent{\centering\includegraphics[width=0.95\linewidth]{table.png}\\}

\begin{multicols}{2}
\noindent{\centering\includegraphics[width=1.15\linewidth]{pdfs/screenshot4.png}\\}
\begin{itemize}\compresslist
\item Techniques for field type refinement.
\item Formalization and proofs.
\item Case studies and applications.
    \small{\newline
    % \begin{itemize}\compresslist
    % \item The Expression Problem
    % \item Embedded DSLs with Fluent Interfaces
    % \item A Maze Game
    % \item Refactoring an Interpreter
    % \end{itemize}
    [The Expression Problem]\newline
    [Embedded DSLs with Fluent Interfaces]\newline
    [A Maze Game]\newline
    [Refactoring an Interpreter] 
    }
\end{itemize}
\end{multicols}
}

  \headerbox{Acknowledgments}{name=acknowledge,column=1, span=2, below=more}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This work is sponsored by the Hong Kong Research Grant Council Early Career 
Scheme project number 27200514. The first and second authors are supported by 
the SIG PAC student travel grant.
  }

  \headerbox{Contacts}{name=acknowledge,column=1,span=2,below=acknowledge,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{The University of Hong Kong} \\
Yanlin Wang, Haoyuan Zhang, Bruno C. d. S. Oliveira: \emph{\{ylwang,hyzhang,bruno\}@cs.hku.hk} \\
\newline
\textbf{Victoria University of Wellington} \\
Marco Servetto: \emph{marco.servetto@ecs.vuw.ac.nz}
}

>>>>

  \headerbox{Contributions}{name=contribution,column=0,below=motivation}{
  \noindent \begin{enumerate}\compresslist
		\item A formalization of the hierarchical dispatching algorithm
		\item Hierarchical overriding: override individual branches of the class hierarchy.
		\item FHJ: a formalized model based on Featherweight Java
		\item Prototype implementation: FHJ interpreter in Scala.
   \end{enumerate}
   \vspace{0.3em}
  }

\headerbox{Real Conflicts}{name=implementation,column=0,below=contribution}{

\noindent{\centering\includegraphics[width=5em]{../ECOOP18/pics/P1.pdf}\\}
\vspace{0.5em}
\noindent{\centering\includegraphics[width=5em]{../ECOOP18/pics/P4.pdf}\\}
\vspace{0.1em}

\begin{enumerate}
\item Real conflicts needs to be explicitly resolved by programmers. \\
\item Existing OOP models have taken care of this case intensively.
\end{enumerate}
% \begin{figure*}
% \begin{tabular}{clcl}
% &\multicolumn{1}{c}{\includegraphics[width=5em]{../ECOOP18/pics/P1.pdf}} & & 
% \multicolumn{1}{c}{\includegraphics[width=5em]{../ECOOP18/pics/P4.pdf}}\\
% \end{tabular}
% \end{figure*}
}

  \headerbox{Unintentional Conflicts}{name=uml,column=0,below=implementation,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent{\centering\includegraphics[width=\linewidth]{../ECOOP18/pics/conflicts.png}\\}
\vspace{0.1em}
\begin{enumerate}
\item Conflicting methods have completely different meaning/domain which just share the same name (and parameter types). 
\item Few existing OOP models support unintentional method conflicts well. 
\end{enumerate}
}

\begin{comment}  
  \headerbox{Results (Partial)}{name=result,column=0,below=uml,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the maze game case study, both SLOC and \# of interfaces are greatly reduced:
\noindent{\centering\includegraphics[width=0.81\linewidth]{pdfs/result.png}\\}
\vspace{0.1em}
}
\end{comment}

\vspace{-0.5em}
\headerbox{P1: basic unintentional method conflicts}{name=Model,column=1,span=2,row=0}{
\lstinputlisting[linerange=1-6]{./src/src1.txt}
}

\vspace{-0.5em}
\headerbox{P2: dynamic dispatching}{name=results,column=1,span=2,row=0,below=Model}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \begin{multicols}{2}
%  \noindent{\centering\includegraphics[width=1\linewidth]{images/mymodel.pdf}\\}
% The process of generating an academic document is as follows: for each citation in that document, firstly sample a topic $\topic_k$ according to the distribution from paper\_topic distribution $\delta(\topic ; \paper)$ or author\_topic distribution $\zeta(\topic ; \authorvar)$ or venue\_topic distribution $\psi(\topic ; \venue)$  based on the document type. Then, draw a citation $\citationvar$ from the sampled topic distribution $\phi(:;\topic_k)$ in topic\_citation distribution $\phi(\citationvar;\topic)$.
% \end{multicols}

\lstinputlisting[linerange=9-17]{./src/src1.txt}
}

@@

\headerbox{P3: overriding on individual branches}{name=with,column=1,span=2,row=0,below=results}{

\lstinputlisting[linerange=20-29]{./src/src1.txt}
}

\vspace{-0.5em}
\headerbox{Syntax}{name=syntax,column=1,span=2,row=0,below=with}{
\noindent{\includegraphics[width=0.9\linewidth]{pdfs/syntax.png}}
}
\vspace{-0.5em}

\headerbox{The Key Semantics Rule}{name=semantics,column=1,span=2,row=0,below=syntax}{
\noindent{\includegraphics[width=0.85\linewidth]{pdfs/semantics2.png}}
}
\vspace{-0.5em}

\headerbox{More in the paper}{name=more,column=1,span=2,row=0,below=semantics}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}
\begin{itemize}
\item Intuitive examples
\item Subtyping, typing and reduction rules
\item Design choices
\item Extensions
\item Properties/Proofs
\item ...
\end{itemize}
\end{multicols}
% \noindent{\centering\includegraphics[width=0.95\linewidth]{table.png}\\}

% \begin{multicols}{2}
% \noindent{\centering\includegraphics[width=1.15\linewidth]{pdfs/screenshot4.png}\\}
% \begin{itemize}\compresslist
% \item Techniques for field type refinement.
% \item Formalization and proofs.
% \item Case studies and applications.
%     \small{\newline
%     % \begin{itemize}\compresslist
%     % \item The Expression Problem
%     % \item Embedded DSLs with Fluent Interfaces
%     % \item A Maze Game
%     % \item Refactoring an Interpreter
%     % \end{itemize}
%     [The Expression Problem]\newline
%     [Embedded DSLs with Fluent Interfaces]\newline
%     [A Maze Game]\newline
%     [Refactoring an Interpreter] 
%     }
% \end{itemize}
% \end{multicols}
}

%   \headerbox{Acknowledgments}{name=acknowledge,column=1, span=2, below=more}{
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is sponsored by the Hong Kong Research Grant Council Early Career 
% Scheme project number 27200514. The first and second authors are supported by 
% the SIG PAC student travel grant.
%   }

  \headerbox{Contacts}{name=acknowledge,column=1,span=2,below=more,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{The University of Hong Kong} \\
Yanlin Wang, Haoyuan Zhang, Bruno C. d. S. Oliveira: \emph{\{ylwang,hyzhang,bruno\}@cs.hku.hk} \\
\newline
\textbf{Victoria University of Wellington} \\
Marco Servetto: \emph{marco.servetto@ecs.vuw.ac.nz}
}
